A Motion Capture and Imitation Learning-based Approach to Robot Control

### 2022-06-22 tex-arxiv/article.tex
proposed approach tentative

The next crucial decision to make is

>>>>

The next crucial decision to make is what the input and output spaces of the model will be. Setting aside the additional control parameters (target coordinates and release signal), when provided with a sequence of pose observations the main options are:
\begin{itemize}
	\item Pose-Pose -- predict the pose at the next discrete time step from the current observation;
	\item Pose-Derivatives -- predict velocities or accelerations as actions;
	\item Joint state-Joint target -- analogous to pose-pose, but in joint space;
	\item Joint state-Joint velocity -- analogous to pose-derivates, but in joint space.
\end{itemize}

Approaches crossing the Cartesian-joint space domain boundary were not considered, as the model would be required to learn the inverse kinematics of the robot. The advantages of having a model operate entirely in joint space would be seen at the next stage -- integration with the robot controller -- as motion planning to joint targets is trivial. However, training such a model would require mapping the demonstrations to robot configuration space by solving inverse kinematics on them, much the same as with a model operating in Cartesian space. While computationally less expensive at runtime, this approach is more difficult to reason about or explain, complicating the hyperparameter discovery process. Any model obtained this way would also be tightly coupled to a specific robot. Hence, all models were trained in Cartesian space, with the motion planning step left for last.

Outputting pose derivatives (linear and angular velocities) is advantageous as it enables the use of servo controllers, should implementations of such exist, and input-output timing constraints are less stringent than they would be in a strict sequence model that assumes a constant time step. However, a model-in-the-loop control scheme is required~-- forward planning is not possible without a means to integrate model outputs with realistic feedback from the environment. Moreover, for training the model derivatives of the pose need to be estimated from sequential observations, highly susceptible to discretization error.

Predicting the future pose allows for using discrete-time pose observations directly, and, assuming a pose following controller is able to keep within tolerance, forward planning becomes a matter of running the model autoregressively (using its own outputs for generating a sequence). This approach naturally lends itself to the employment of recurrent model architectures. The main drawback is that pose derivative information is encoded in the time step, which imposes constraints on observation and command timing, complicating use of such a model in a real-time feedback manner. It also requires that a method for accurate time parametrization of Cartesian motion plans is available. Ultimately this is the approach that was selected, because it neatly decouples the model and its generated plans from a specific robot implementation, and enables us to generate, visualize and numerically evaluate motion plans ahead of time. Execution then becomes a matter of conventional motion planning given a Cartesian path.
